Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-04-17 ms.tex
added a histo plot for K1255 amplitudes.

>>>>

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_histogram.pdf}
\caption{Histogram of transit amplitudes.
An amplitude of 1.0 corresponds to the average light curve (with flux minimum of 99.53\% or 0.47\% transit depth).
A comparison histogram is shown from the Kepler Secondary eclipses to show the photon noise.}\label{fig:secEclipse}
\end{centering}
\end{figure*}
